Rigidity of Expectations: Additional Evidence from Density Forecasts of Professionals and Households

### 2019-07-18 paper/Draft.tex
Added 3000 articles of NYT

	Second, \citet{manski2004measuring}, \citet{delavande2011measuring} and many other papers have advocated long for eliciting probabilistic questions measuring subjective uncertainty in economic surveys. Although the initial suspicion concerning to people's ability in understanding, using and answering probabilistic questions is understandable, \citet{bertrand2001people} and other work have shown respondents have consistent ability and willingness to assign a probability (or “percent chance”) to future events. \citet{armantier2017overview} have a thorough discussion on designing, experimenting and implementing the consumer expectation surveys to insure the quality of the responses\footnote{Other literature includes \citet{van2008rethinking} and \citet{delavande2014probabilistic}, etc.}. Broadly speaking, the advocators have argued that going beyond the revealed preference approach, availability to survey data provides economists with direct information on agents' expectations and helps avoids imposing arbitrary assumption.  This insight holds for not only point forecast, but also and even more importantly, for uncertainty, because for any economic decision made by a risk-averse agent, not only the expectation but also the perceived risks matter a great deal.

	Third, by approximating subjective uncertainty directly from density responses, this paper contributes to the literature that develops and uses a variety of measures of uncertainty, especially in the macroeconomic context. There is a long tradition of approximating uncertainty by measures that are more directly available in survey data or that can be estimated by econometric methods. For instance, \citet{bachmann2013uncertainty} use ex ante disagreement and ex post forecast errors computed from forecasters' surveys as proxies of uncertainty. \citet{jurado2015measuring} define the time-varying uncertainty as conditional volatility of the unforecastable component of a macroeconomic variable and estimate it using multiple series of macroeconomic variables. \citet{binder2017measuring} approximate uncertainty from rounding in survey data based on the insights from cognitive literature. Besides, an emerging approach such as \citet{bloom2009impact} constructs indices of policy uncertainty based on texts of newspaper reporting. Although these proxies are all meant to capture the notion of uncertainty,  as shown in the Section \ref{StylizedFacts}, a cross-validation seems to suggest they are statistically uncorrelated or even negatively correlated.

>>>>

	Second, \citet{manski2004measuring}, \citet{delavande2011measuring}, \citet{manski2018survey} and many other papers have advocated long for eliciting probabilistic questions measuring subjective uncertainty in economic surveys. Although the initial suspicion concerning to people's ability in understanding, using and answering probabilistic questions is understandable, \citet{bertrand2001people} and other work have shown respondents have consistent ability and willingness to assign a probability (or “percent chance”) to future events. \citet{armantier2017overview} have a thorough discussion on designing, experimenting and implementing the consumer expectation surveys to insure the quality of the responses\footnote{Other literature includes \citet{van2008rethinking} and \citet{delavande2014probabilistic}, etc.}. Broadly speaking, the advocators have argued that going beyond the revealed preference approach, availability to survey data provides economists with direct information on agents' expectations and helps avoids imposing arbitrary assumptions.  This insight holds for not only point forecast, but also and even more importantly, for uncertainty, because for any economic decision made by a risk-averse agent, not only the expectation but also the perceived risks matter a great deal.

	Third, by approximating subjective uncertainty directly from density responses, this paper contributes to the literature that develops and uses a variety of measures of uncertainty, especially in the macroeconomic context. There is a long tradition of approximating uncertainty by measures that are more directly available in survey data or that can be estimated by econometric methods. For instance, \citet{bachmann2013uncertainty} use ex ante disagreement and ex post forecast errors computed from forecasters' surveys as proxies of uncertainty. \citet{jurado2015measuring} define the time-varying uncertainty as conditional volatility of the unforecastable component of a variable and estimate it using multiple macroeconomic series. \citet{binder2017measuring} approximate uncertainty from rounding in survey data based on the insights from cognitive literature. Besides, the text-based approach such as \citet{bloom2009impact} constructs indices of policy uncertainty based on texts of newspaper reporting. Although these proxies are all meant to capture the notion of uncertainty,  as shown in the Section \ref{StylizedFacts}, a cross-validation seems to suggest they are statistically uncorrelated or even negatively correlated.
